\bf Adaption of the Chumbley Score to matching of bullet striation marks

### 2018-01-03 short/short.tex
short version added

---
title: "Adaption of the Chumbley Score to matching of bullet striation marks"
authors:
- affiliation: Department of Statistics, Iowa State University 
  name: Ganesh Krishnan
  thanks: The authors gratefully acknowledge ...
- affiliation: Department of Statistics and CSAFE, Iowa State University 
  name: Heike Hofmann
biblio-style: apsr
output:
  pdf_document:
    citation_package: natbib
    fig_caption: yes
    keep_tex: yes
    latex_engine: pdflatex
    template: template.tex
  html_document: default
blinded: 0
keywords:
- Bullets, Signatures, Lands, Errors, Known match, Known non-match, Comparisons
bibliography: bibliography
<!-- abstract: null -->
---

@@

<!-- \tableofcontents -->

```{r setup, echo = FALSE, message = FALSE, warning = FALSE}
library(knitr)
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  error = FALSE, 
  collapse = TRUE,
  comment = "",
  fig.height = 6,
  fig.width = 6,
  fig.align = "center",
  out.width= '\\textwidth',
  cache = FALSE,
  fig.path='figures/',
  echo=FALSE,
  cache=TRUE
)
options(knitr.table.format = "latex")
library(tidyverse)
```
# Introduction and Results

@@

An objective analysis of signatures (pre-processed markings) and profiles (raw markings) of bullet lands for all Hamby-44 and Hamby-252 scans pairwise land to land comparisons (a total of 85,491 comparisons)\citep{hamby} made available through the NIST ballistics database \citep{nist} was done to identify the effects of the two comparison windows and coarseness parameter on the error rates in as proposed in the adjusted chumbley algorithm for toolmarks by \citet{hadler}. The results suggested that the Nominal type I error $\alpha$ value shows dependency on the size of the window of optimization and the window of validation. For a given window of optimization the actual Type I error is comparable the nominal level only for only a select few validation window sizes.
A Test Fail, which is the percentage of incorrect classifications, depends on whether known-match or known non-matches has predictive value, with test results from different sources having a much higher chance to fail. On conducting an analysis of all known bullet lands using the adjusted chumbley algorithm, Type II error was identified to be least bad for window of validation 30 and window of optimization 120. In case of unsmoothed raw marks (profiles), Type II error increases with the amount of smoothing and least for LOWESS smoothing coarseness value about 0.25 or 0.3. In an effort to identify the level of adaptiveness of the algorithm, comparisons were made between signatures and profiles. Their comparison with respect to validation window size for a fixed optimization window side suggeted that, profiles have a total error greater than or equal to the total error of signatures for all sizes of validation window. Profiles also fail (i.e. incorrectly classify known-matches and known non-matches) more number of times than signatures, which lets us conclude that the behaviour of the algorithm for the profiles instead of pre-processed signatures is not better. Finally it needs to be noted that the current version of the adjusted chumbley algorithm seems to falls short when compared to other machine-learning based methods \citet{aoas}, and some level of modification to the deterministic algorithm needs to be identified and tested that would reduces the number of incorrect classifications.

>>>>

% !TeX program = pdfLaTeX
\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{graphicx,psfrag,epsf}
\usepackage{enumerate}
\usepackage{natbib}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage[table]{xcolor}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{hyperref}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}

\usepackage{url} % not crucial - just used below for the URL

%\pdfminorversion=4
% NOTE: To produce blinded version, replace "0" with "1" below.
\newcommand{\blind}{0}

% DON'T change margins - should be 1 inch all around.
\addtolength{\oddsidemargin}{-.5in}%
\addtolength{\evensidemargin}{-.5in}%
\addtolength{\textwidth}{1in}%
\addtolength{\textheight}{1.3in}%
\addtolength{\topmargin}{-.8in}%

\newenvironment{definition}[1]% environment name 
{% begin code 
  \par\vspace{.75\baselineskip}\noindent 
  \textbf{Definition (#1)}\begin{itshape}% 
  \par\vspace{.5\baselineskip}\noindent\ignorespaces 
}% 
{% end code 
  \end{itshape}\ignorespacesafterend 
}

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\begin{document}

\def\spacingset#1{\renewcommand{\baselinestretch}%
{#1}\small\normalsize} \spacingset{1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\if0\blind
{
  \title{\bf Adaption of the Chumbley Score to matching of bullet striation marks}

  \author{
        Ganesh Krishnan \thanks{The authors gratefully acknowledge \ldots{}} \\
    Department of Statistics, Iowa State University\\
     and \\     Heike Hofmann \\
    Department of Statistics and CSAFE, Iowa State University\\
      }
  \maketitle
} \fi

\if1\blind
{
  \bigskip
  \bigskip
  \bigskip
  \begin{center}
    {\LARGE\bf Adaption of the Chumbley Score to matching of bullet striation marks}
  \end{center}
  \medskip
} \fi

\bigskip
% \begin{abstract}
% 
% \end{abstract}

\noindent%
{\it Keywords:} Bullets, Signatures, Lands, Errors, Known match, Known non-match,
Comparisons
\vfill

\newpage
\spacingset{1.45} % DON'T change the spacing!

@@

\section{Introduction and Results}\label{introduction-and-results}

@@

An objective analysis of signatures (pre-processed markings) and
profiles (raw markings) of bullet lands for all Hamby-44 and Hamby-252
scans pairwise land to land comparisons (a total of 85,491
comparisons)\citep{hamby} made available through the NIST ballistics
database \citep{nist} was done to identify the effects of the two
comparison windows and coarseness parameter on the error rates in as
proposed in the adjusted chumbley algorithm for toolmarks by
\citet{hadler}. The results suggested that the Nominal type I error
\(\alpha\) value shows dependency on the size of the window of
optimization and the window of validation. For a given window of
optimization the actual Type I error is comparable the nominal level
only for only a select few validation window sizes. A Test Fail, which
is the percentage of incorrect classifications, depends on whether
known-match or known non-matches has predictive value, with test results
from different sources having a much higher chance to fail. On
conducting an analysis of all known bullet lands using the adjusted
chumbley algorithm, Type II error was identified to be least bad for
window of validation 30 and window of optimization 120. In case of
unsmoothed raw marks (profiles), Type II error increases with the amount
of smoothing and least for LOWESS smoothing coarseness value about 0.25
or 0.3. In an effort to identify the level of adaptiveness of the
algorithm, comparisons were made between signatures and profiles. Their
comparison with respect to validation window size for a fixed
optimization window side suggeted that, profiles have a total error
greater than or equal to the total error of signatures for all sizes of
validation window. Profiles also fail (i.e.~incorrectly classify
known-matches and known non-matches) more number of times than
signatures, which lets us conclude that the behaviour of the algorithm
for the profiles instead of pre-processed signatures is not better.
Finally it needs to be noted that the current version of the adjusted
chumbley algorithm seems to falls short when compared to other
machine-learning based methods \citet{aoas}, and some level of
modification to the deterministic algorithm needs to be identified and
tested that would reduces the number of incorrect classifications.

\bibliographystyle{agsm}
\bibliography{bibliography}

\end{document}
